---
title: "TITLE OF DOCUMENT"
additional1: "ADDITIONAL LINE 1"
additional2: "ADDITIONAL LINE 2"
subtitle: "Subtitle of Document"
projectname: "Name of Project/Mandate, etc..."
author:
  - name: Jane Doe
    affiliation: University of Basel
    email: jane.doe@unibas.ch
  - name: Sam Smith
    affiliation: Swiss TPH
    email: sam.smith@swisstph.ch
format:
  report-typst:
    section-numbering: "1.1.1"
numbering: 1
date: last-modified
fontsize: 11pt
lang: en
execute: 
  echo: false
  warning: false
toc: true
toc-depth: 3
bibliography: references.bib
---

<!--
================================================================================
GUIDE TO THE YAML HEADER ABOVE  (this block is a comment; it does NOT render)
================================================================================

This is the TYPST version of the report. Typst has its own built-in engine, so
there is NO pdf-engine line and NO machine-specific font path — the Aptos font
is set inside the extension (_extensions/report/), so this file renders the
same on any machine. (Typst falls back gracefully if Aptos is not installed.)

SAFE TO CUSTOMISE — change these freely (all are text on the cover / body):

  title:        Main document title.
  additional1 / additional2:
                Two extra free-text lines on the cover page (custom Swiss TPH
                fields). Keep both keys present even if you leave one empty.
  subtitle:     Document subtitle.
  projectname:  Project / mandate name shown on the cover.
  author:       List of authors. Edit values (name, affiliation, email) and
                add/remove whole entries. KEEP the "- name:" structure.
  date:         "last-modified" auto-fills from the file's mtime. Can be a
                fixed date (e.g. 2026-06-15) or removed.
  fontsize:     Base text size (e.g. 11pt, 12pt).
  lang:         Document language (e.g. en, de, fr).
  toc:          true/false — show the table of contents. Safe to flip.
  toc-depth:    How many heading levels appear in the TOC.
  section-numbering: "1.1.1"
                Heading-numbering scheme. "1.1.1" = numerals at every level.
                e.g. "1.A.a" would number subsections with letters. Safe to
                edit; set to "" or remove to switch numbering off.
  numbering: 1  Page-numbering style (1 = arabic numerals).

CHANGE ONLY IF YOU KNOW WHAT YOU ARE DOING — these can break rendering:

  format: report-typst
                The Swiss TPH Typst extension (lives in _extensions/report/).
                Supplies the cover page, colours, font, and layout. Do NOT
                rename, move, or delete _extensions/.

  execute: { echo: false, warning: false }
                Hides R code and warnings. echo: true dumps R source into the
                PDF body.

  bibliography: references.bib
                Citation source for @-references. Keep references.bib in this
                working directory, or citations fail to resolve.
================================================================================
-->

```{r}
# Put a R chunk here even if you don't need it
# to make sure the rendering works well
```


<!-- COVER PAGE SEE "_extensions/report/before-body.tex" -->



<!-- MAIN PART -->

\newpage

# EXECUTIVE SUMMARY

```{r}
set.seed(42)
lorem::ipsum(2)
```

# EXAMPLE HEADING 1

```{r}
lorem::ipsum(1)
```

## EXAMPLE HEADING 2

```{r}
lorem::ipsum(2)
```

### EXAMPLE HEADING 3

```{r}
lorem::ipsum(2)
```

#### EXAMPLE HEADING 4

```{r}
lorem::ipsum(1)
```


## Example Table: Flextable

```{r}
#| label: tbl-flextable
#| tbl-cap: "Car Performance Data (mtcars)"
#| tbl-colwidths: auto

# Load required packages
library(flextable)
library(dplyr)

# Prepare data (first 5 rows of mtcars)
data <- head(mtcars, 5) %>% 
  tibble::rownames_to_column("Car Model") %>% 
  select(1:4) # Select first 4 columns for brevity

# Create flextable
ft <- flextable(data) %>%
  # Style headers
  bold(part = "header") %>% 
  bg(part = "header", bg = "#432CA1") %>% 
  color(part = "header", color = "white") %>% 
  # Style body
  bg(bg = "white", part = "body") %>% 
  # Column-specific formatting
  colformat_num(j = c("mpg", "disp"), digits = 1) %>% 
  # Autofit columns
  autofit()

ft
```


@tbl-flextable is an example of using R code to generate a table in Quarto documents.


## Example Chart: ggplot2

```{r}
#| label: fig-ggplot2
#| fig-cap: "Miles Per Gallon (MPG) Distribution"

library(ggplot2)
ggplot(mtcars, aes(x = mpg, fill = factor(cyl))) +
  geom_histogram(
    binwidth = 3, 
    position = "identity", 
    alpha = 0.6
  ) +
  scale_fill_manual(values = c("#432CA1", "#DDE24A", "#EA6674"))  # Swiss TPH indigo, yellow, red
```

@fig-ggplot2 is an example of using R code to generate a figure in Quarto documents.

## Example Citations

This example is from @akpodiete_improvement_2025.

Mosquitoes of the *Anopheles gambiae* s.l. complex are the primary vectors of human malaria in sub-Saharan Africa. The freshwater species *Anopheles coluzzii* is one of this complex’s most abundant and widespread vectors. It is found from Senegal to Angola, spanning West Africa, West-Central Africa, and North-West Southern Africa (@della_torre_distribution_2005, @gimonneau_behavioral_2010)

For more advanced use of Quarto citations, see [Citations - Quarto](https://quarto.org/docs/authoring/citations.html).

# TIPS AND TRICKS

## Swiss TPH self-paced Quarto tutorial

See [Swiss TPH Quarto training](https://research-it-swiss-tph.github.io/quarto_training/) for the Quarto tutorial website developed by Research Informatics.

## Callout blocks in Quarto

You can create colourful callout blocks in Quarto very easily.

::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {#refs}
:::
